*Catchy short title*: \\ automated noise processing for near-surface characterization with seismic data from a fiber network

### 2017-02-14 paper.tex
Word count, paragraph assignment, figure count

\begin{abstract} 
*****abstract words here *****
\end{abstract}

\section*{Motivation}
****what's ambient noise used for?****

@@

\section*{New Contributions}
****what's new that we're doing, how it's different from what's been done before****

\section*{Background Theory}
****ambient noise background****

\section*{Experimental Overview}
****overview of the array, potential noise sources, ambient noise field****

\section*{Data Processing}
***overview of data processing workflow****

\subsection*{Estimating Sensor Coupling Response}
***talk about different responses from different sensors and how to compensate for these, use many earthquakes for relative responses****

\subsection*{Localizing Persistent Noise Sources}
***talk about localizing these things (motors, traffic, etc....) and show a little beamforming in small 1D parts of the array bandpassed to these persistent frequency peaks***

\subsection*{Removing Earthquakes and Quarry Blasts}
****talk about getting rid of big events lighting up whole array****

\subsection*{Removing Vehicle Noise}
****talk about clustering and comparing noise sources-including rotations and stretch of example noise****

\subsection*{Removing Correlated Noise Sources}
*****talk about detecting temporally and spatially correlated noise sources, more generally than cars****

\subsection*{Traveltime Picking}
*** talk about traveltime picking before Rayleigh wave tomography****

\subsection*{Tomography}
**** talk about how near-surface tomography is set up****

\section*{Results}
***overview of results****

\subsection*{Convergence Rate Improvement Due to Pre-Processing}
***show comparisons of cross-correlations with/without sensor coupling response, and with scaling by energy per channel of cross-correlations (also show spectrum per channel of these)****
\\
******show comparisons of convergence rates with/without vehicles removed, and with vehicles just removed via STA/LTA jumps****

\subsection*{Tomography Along Array Lines}
***show tomography results along multiple lines on campus****

\section*{Summary}
****summary words****

>>>>

\begin{abstract} 
*****abstract words here - 150-200 Eileen*****
\end{abstract}

\section*{Motivation}
****what's ambient noise used for? - 200-250 Eileen****

@@

\section*{New Contributions}
****what's new that we're doing, how it's different from what's been done before - 150 Eileen, little Fantine & Yinbin****

\section*{Background Theory}
****ambient noise background - 150-220 Eileen****

\section*{Experimental Overview}
****overview of the array, potential noise sources, ambient noise field - 200 Eileen****
****Figure : 2 panels: Installation + map****

\section*{Data Processing}
***overview of data processing workflow - 200-250 Eileen****
***Figure : stft plots at a few different spots***
***Mention whitening here***
***Mention earthqukes and quarry blasts here***

\subsection*{Estimating Sensor Coupling Response}
***talk about different responses from different sensors and how to compensate for these, use many earthquakes for relative responses****
***100 Eileen***
***Figure : Boxed earthquake recording + response versus channel***

% \subsection*{Localizing Persistent Noise Sources}
% ***talk about localizing these things (motors, traffic, etc....) and show a little beamforming in small 1D parts of the array bandpassed to these persistent frequency peaks***

% \subsection*{Removing Earthquakes and Quarry Blasts}
% ****talk about getting rid of big events lighting up whole array****

\subsection*{Removing Vehicle Noise}
****talk about clustering and comparing noise sources****
***500 Fantine & Yinbin***
***Figures : Before/after car mute + clusters and projection on map***
***Little Eileen for sentence about why cars are a problem***

% \subsection*{Removing Correlated Noise Sources}
% *****talk about detecting temporally and spatially correlated noise sources, more generally than cars****

% \subsection*{Traveltime Picking}
% *** talk about traveltime picking before Rayleigh wave tomography****
% *** STANDBY ***

% \subsection*{Tomography}
% **** talk about how near-surface tomography is set up****
% *** STANDBY ***

\section*{Results}
***overview of results****
*** Convergence rates
***150 Eileen *** 
***Figure : line plot of correlation coeeficients vs epoch/time***

% \subsection*{Convergence Rate Improvement Due to Pre-Processing}
***show comparisons of cross-correlations with/without sensor coupling response, and with scaling by energy per channel of cross-correlations (also show spectrum per channel of these)****
\\
******show comparisons of convergence rates with/without vehicles removed, and with vehicles just removed via STA/LTA jumps****

% \subsection*{Tomography Along Array Lines}
% ***show tomography results along multiple lines on campus****
% *** STANDBY ***

\section*{Summary}
****summary words****
***100 Eileen ***
